Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-08-27 code/analysis.Rmd
fixed k_s

Or, expressed for $k_s$, $$k_s = \frac{m_s}{m_0}(1-e^{-kT})k_{tot}$$

@@

final <- trapfinal %>%
  group_by(date) %>%
  summarise(m_trap = mean(sed)/1000) %>% #average sediment in trap converted from mg to g
  mutate(m_s = m_trap*1.95*.6/(pi*.0127^2)) %>% #times test section area divided by area of 1 trap
  left_join(fitdata, by = "date") %>%
  mutate(k_s = m_s/200*(1-exp(t*6000))*(-t))

>>>>

Or, expressed for $k_s$, $$k_s = \frac{m_s}{m_0}(\frac{1}{1-e^{-kT}})k_{tot}$$

@@

final <- trapfinal %>%
  group_by(date) %>%
  summarise(m_trap = mean(sed)/1000) %>% #average sediment in trap converted from mg to g
  mutate(m_s = m_trap*1.95*.6/(pi*.0127^2)) %>% #times test section area divided by area of 1 trap
  left_join(fitdata, by = "date") %>%
  mutate(k_s = m_s/200/(1-exp(t*6000))*(-t))
